true

### 2020-04-27 analysis/robinson2020.Rmd
getting travis working

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."), recursive = TRUE)
  unlink(here::here("analysis/data/derived_data/."), recursive = TRUE)
}
```

@@

## Datasets {-}
```{r prepare-radiocarbon-data}
# Read in the radiocarbon database
# Filter the 2-sigma calibrated ranges to the trunc_dates range
if (!file.exists(
  here::here("analysis/data/derived_data/radiocarbon_data.csv")
)) {
  readr::read_csv(
    here::here("analysis/data/raw_data/robinson_et_al_2020_radiocarbon.csv")
  ) %>%
    dplyr::mutate(
      Type = "Radiocarbon",
      Site_ID = Site_ID %>% stringr::str_c("Radiocarbon - ", .)
    ) %>%
    dplyr::select(
      Type,
      SiteID = Site_ID,
      Site_Number,
      County,
      Lab_Number,
      Date_BP,
      SD
    ) %>%
    # retain dates whose calibrated 95% probability mass overlaps trunc_dates
    dplyr::filter(
      rcarbon::calibrate(
        x = Date_BP,
        errors = SD,
        verbose = FALSE
      ) %>%
        rcarbon:::hpdi(credMass = 0.95) %>%
        purrr::map_lgl(function(x) {
          startdate <- max(x[, "startCalBP"])
          enddate <- min(x[, "endCalBP"])
          startdate > trunc_dates[[2]] && enddate <= trunc_dates[[1]]
        })
    ) %>%
    # Write the output to a new file (csv)
    readr::write_csv(
      here::here("analysis/data/derived_data/radiocarbon_data.csv")
    )
}

>>>>

if (params$clean) {
  unlink(here::here("analysis/robinson2020.pdf"))
  unlink(here::here("analysis/robinson2020_cache"), recursive = TRUE)
  unlink(here::here("analysis/figures/."))
  unlink(here::here("analysis/data/derived_data/."))
}
```

@@

## Datasets {-}
```{r prepare-radiocarbon-data}
# Read in the radiocarbon database
# Filter the 2-sigma calibrated ranges to the trunc_dates range
if (!file.exists(
  here::here("analysis/data/derived_data/radiocarbon_data.csv")
)) {
  download.file("https://core.tdar.org/filestore/download/455460/567756",
    destfile = here::here("analysis/data/raw_data/robinson_et_al_2020_radiocarbon.csv")
  )

  readr::read_csv(
    here::here("analysis/data/raw_data/robinson_et_al_2020_radiocarbon.csv")
  ) %>%
    dplyr::mutate(
      Type = "Radiocarbon",
      Site_ID = Site_ID %>% stringr::str_c("Radiocarbon - ", .)
    ) %>%
    dplyr::select(
      Type,
      SiteID = Site_ID,
      Site_Number,
      County,
      Lab_Number,
      Date_BP,
      SD
    ) %>%
    # retain dates whose calibrated 95% probability mass overlaps trunc_dates
    dplyr::filter(
      rcarbon::calibrate(
        x = Date_BP,
        errors = SD,
        verbose = FALSE
      ) %>%
        rcarbon:::hpdi(credMass = 0.95) %>%
        purrr::map_lgl(function(x) {
          startdate <- max(x[, "startCalBP"])
          enddate <- min(x[, "endCalBP"])
          startdate > trunc_dates[[2]] && enddate <= trunc_dates[[1]]
        })
    ) %>%
    # Write the output to a new file (csv)
    readr::write_csv(
      here::here("analysis/data/derived_data/radiocarbon_data.csv")
    )
}
